\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-23 papers/jss/article.Rnw
another pass at the summary
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@841 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Summary}  % DE Simpler title
\label{sec:summary}
Over the past decade, many formats for interoperable
data exchange have become available, each with their unique features,
strengths and weaknesses.  
Text based formats such as CSV and JSON are easy to use, and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex analysis stacks and applications involving 
distributed computing as well as mixed language analysis pipelines, choosing a more 
sophisticated data interchange format may reap considerable benefits. 
The Protocol Buffers protocol and library offers a unique combination of features, performance,
maturity, and forward-compatibility that seems particulary well suited for data-driven 
applications and numerical computing.

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers library, and
extends the \proglang{R} system with the ability to create, read,
write, parse, and manipulate Protocol
Buffer messages. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts, and software engineers.
At the time of this writing there are more than 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with distributed systems written in \proglang{C++}, \proglang{Java}, \proglang{Python}, and 
other languages.  It is our hope that this
package will make Protocol Buffers more accessible to the \proglang{R} community, and
thereby makes a small contribution towards better integration between \proglang{R} and
other software systems and applications.

>>>>

\section{Summary}  % DE Simpler title
\label{sec:summary}
Over the past decade, many formats for interoperable
data exchange have become available, each with their unique features,
strengths and weaknesses.  
Text based formats such as \texttt{CSV} and \texttt{JSON} are easy to use, and will likely 
remain popular among statisticians for many years to come. However, in the 
context of increasingly complex analysis stacks and applications involving 
distributed computing as well as mixed language analysis pipelines, choosing a more 
sophisticated data interchange format may reap considerable benefits. 
%Protocol Buffers is itself not a protocol.
%Forward-compatibility is one of the features. No need to re-iterate those 
The Protocol Buffers standard and library offer a unique combination of features, 
performance, and maturity, that seems particulary well suited for data-driven 
applications and numerical computing.

%% DE Re-ordering so that we end on RProtoBuf
The \pkg{RProtoBuf} package builds on the Protocol Buffers \proglang{C++} library, 
and extends the \proglang{R} system with the ability to create, read,
write, parse, and manipulate Protocol
Buffer messages. \pkg{RProtoBuf} has been used extensively inside Google 
for the past three years by statisticians, analysts, and software engineers.
At the time of this writing there are over 300 active
users of \pkg{RProtoBuf} using it to read data from and otherwise interact
with distributed systems written in \proglang{C++}, \proglang{Java}, \proglang{Python}, and 
other languages. We hope that making Protocol Buffers available to the
\proglang{R} community will contribute towards better software integration
and allow for building even more advanced applications and analysis pipelines 
with \proglang{R}.
